---
title: "experiments"
output: html_notebook
---

Load all necessary user-defined functions

```{r echo = T, results = 'hide'}
source("./src/utils.R")
source("./src/selectors.R")
```

Load all external libraries.
```{r echo = T, results = 'hide'}
library(jsonlite)
library(progress)
library(lubridate)
library(utiml)
library(dplyr)
library(hash)
library(log4r)
library(mldr.datasets)
```

```{r}
SEED = 0
BUDGET = 20
```


```{r}
data = flags$dataset
X_all = data %>% select(1:19) %>% mutate_if(is.character, as.factor)
Y_all = data %>% select(20:26) %>% mutate_if(is.character, as.factor)

data_splited = train_test_split(X_all, Y_all, test_size = 0.1, seed=SEED)
X_train = data_splited$X_train
Y_train = data_splited$Y_train
X_test = data_splited$X_test
Y_test = data_splited$Y_test

costs = c(
  1,1,1,
  2,2,2,
  3,3,3,
  4,4,4,
  5,5,5,
  6,6,6,
  7
)
```

```{r}
costs
```

```{r}
target_idx <- ncol(X_train) + seq(1, ncol(Y_train))
mldr_dataset_train <- mldr_from_dataframe(cbind(X_train, Y_train), target_idx)
mldr_dataset_test <- mldr_from_dataframe(cbind(X_test, Y_test), target_idx)
```

```{r}
results_df <- data.frame(matrix(ncol = 29, nrow = 0))
colnames(results_df) <- c(
  "criterion", "lambda", "cost", "budget", 
  "accuracy", "average.precision", "clp", "coverage", "F1", 
  "hamming.loss", "macro.AUC", "macro.F1", "macro.precision", "macro.recall", 
  "margin.loss", "micro.AUC", "micro.F1", "micro.precision", "micro.recall", "mlp", 
  "one.error", "precision", "ranking.loss", "recall", "subset.accuracy", "wlp", "selection_type", 
  "budget_pct", "k"
)
```

```{r}
results <- score_final_feature_selection_revision(mldr_dataset_train, mldr_dataset_test, costs, BUDGET)
results
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
